\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2014-08-14 doc/sw-system.tex
Added ROC curves to paper

We now quantify the performance of the \sw system in terms of the recovery of
the training set images. \Fref{fig:results:sample:roc} shows receiver
operating characteristic (ROC) curves for CFHTLS stage 1 and stage 2.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/roc.png}
\caption{Receiver operating characteristic curves for the \sw system, using
the CFHTLS training set.}
\label{fig:results:sample:roc}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

We now quantify the performance of the \sw system in terms of the recovery of
the training set images. \Fref{fig:results:sample:roc} shows receiver
operating characteristic (ROC) curves for CFHTLS stage 1 and stage 2. These
plots show the true positive rate (TPR), the number of sims correctly detected
divided by the total number of sims in the training set, and the false
positive rate (FPR), the number of duds incorrectly detected  divided by total
number of duds in the training set, both for a given sample of detections defined by
a particular probability threshold, which varies along the curves.  In both
stages, these curves show that true positive rates of  around 90\% were
achieved, at very low false positive rates. For comparison we show the results
of an analysis where the classifications of  training images were ignored, and
none of the agents allowed to learn: they were instead assigned initial values
of their confusion matrices of 0.75 for each element, which then remained
constant. This emulates a very simple unweighted voting scheme, where all
classifications are treated equally. In this case, the TPR remains under 80\%
in stage 1 and 60\% in stage 2, showing the benefit of including training
images and allowing the agents to learn. The choice of initial confusion
matrix is not very important: the same 0.75 initial values applied to normal,
learning agents results in a slightly lower TPR than the default case,
indicating that initializing the system less conservatively results in
slightly worse performance.

The dot-dashed curves show the impact of the offline analysis. At stage 1 the
results are very similar to the online version that was actually run (solid
line), at stage 2 there seems to be some benefit to doing the analysis in this
way. Remarkably, over 85\% TPR is achieved at zero FPR. Alternatively, if one
is willing to accept a false positive rate of 5\%, the true positive rate
rises to over 95\%, showing that some of the sims that were missed in the
online analysis can be recovered by doing the analysis offline. The same is
true at stage 1, but to a much lower degree.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\begin{minipage}{0.45\linewidth}
  \centering\includegraphics[width=\linewidth]{sw-system-figs/stage1_ROC.png}
\end{minipage}\hfill
\begin{minipage}{0.45\linewidth}
  \centering\includegraphics[width=\linewidth]{sw-system-figs/stage2_ROC.png}
\end{minipage}
\caption{Receiver operating characteristic curves for the \sw system, using
the CFHTLS training set. Left: stage 1, right: stage 2.}
\label{fig:results:sample:roc}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Adopting the online stage 1 analysis, and the offline stage 2 analysis, we
show in \Fref{fig:results:sample:CP} a plot of completeness versus purity in
the two stages. As in \Fref{fig:results:sample:roc}, the detection threshold
varies along the curves. Completeness is defined as the number of correctly 
detected sims divided by the total number of sims in the training set, while
purity is the number of the number of correctly detected sims divided by the
number of detections that would be claimed in a realistic sample. The purity
can only be calculated approximately. First we compute the expected number of
false positives by multiplying the FPR by the expected number of non-lenses in
the survey. Then we multiply the TPR by the expected number of lenses in the
survey, to get the expected number of true positives. The sum of the true
positives and the false positives gives the expected sample size; dividing the
expected number of true positives by this sample size gives the purity.

\todo{Chris}{Make completeness vs purity plot and add it here, please!}
